---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
h1 {
  
  text-align: center;
}

h2 {
  color: blue;
}

p {
  font-size: 21px;
  line-height: 1.5;
}
```
# Ad Targeting Analysis

## The data from the survey is used to display informative graphs about ad quality and targetting ability


```{r}
library(tidyverse)
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQCRD79AZ4i5kLfX39hGQqFilIeh27TamkTeAuKF2-vToXw2e1pL4nrnchxemf4X_K4oCRPJSMncsg3/pub?output=csv")

latest_data <- logged_data %>% 
  rename(Time=Timestamp, 
      Relevant=Is.this.ad.relevant.to.you...1.being.least.and.5.being.most., 
      Category=What.category.does.the.ad.fall.into., 
      Repeat=Have.you.seen.the.same.or.similar.ad.before.)

mean_relevance <-latest_data$Relevant %>% mean()


yes_repeat <- latest_data[latest_data$Repeat == "Yes",] 
yes_mean_relevance <- yes_repeat$Relevant %>% mean()

no_repeat <- latest_data[latest_data$Repeat == "No",]
no_mean_relevance <- no_repeat$Relevant %>% mean()

total <- length(latest_data)


```

## Bar graph below shows the most common category of instagram ads. Only one category per ad can be selected. The total number of ads is: `r total`

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = Category), fill = "lightblue") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Most common categories", x = "Categories", y = "Count", caption = "Source: google form",
)
```

## Bar graph below shows how relevant ads are to me. The relevancy scale is from 1 to 5 with 1 being the least relevant and 5 being most relevant

```{r}
latest_data %>% 
  ggplot() + geom_bar(aes(x = Relevant) , fill = "#FFDBBB") +
  labs(title = "Number of ads by relevancy",
       caption = "Source: google form",
       x = "Relevant score given")


```

## Ad stats

The ads mean targeting ability is `r round(mean_relevance, 2)` on a scale of 1 to 5.

The ads that have repeated have a relevancy of `r round(yes_mean_relevance, 2)` and the ads that are new
have the relevancy of `r round(no_mean_relevance, 2)`

